---
title: "aa-hex_maps_with_water_points"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-hex_maps_with_water_points}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  collapse = TRUE,
  comment = "#>",
  warning = F, 
  message = F
)
```

```{r, echo=FALSE}
library(here)
library(tidyverse)
devtools::load_all()
theme_set(theme_bw())
library(sf)
library(tmap)
library(leaflet)
```

## Hex Maps with strategic water points

```{r,echo=FALSE}

#' load_h2r_data
#'
#' @return
#' @export
#' @description function to load H2R data set - will use environment key to specify base data directory
#' @examples
load_h2r_data <-  function(main_folder_path, data_path){
  
  # main_folder_path <-  Sys.getenv("SOM_2203_WASH_DATA")
  # data_path <- "data/202209/h2r_aggregated/SOM1901_H2R_hex_400km_May_2022.csv"
  
  h2r_data <- readr::read_csv(file.path(main_folder_path, data_path))# |> 
    # mutate(latitude = parse_number(X),
    #        longitude = parse_number(geometry))
  
  return(h2r_data)
}

#' select_h2r_indicators
#'
#' @return
#' @export
#' @description function to select relevant h2r indicators from data set
#' @examples
select_h2r_indicators <- function(input_df, country_code="som"){
  if(country_code =="som"){
    
    h2r_cols <- c("hex_4000km",
                  "climatic_shock",
                  "crop_loss_reasons",
                  "primary_reason_moved",
                  "idp_new_arrivals",
                  "idp_arrived_reason",
                  "idp_pull_factors",
                  "hc_push_main",
                  "mainsource_water",
                  "responsible_water_fetching",
                  "surfacewater_drinking",
                  "gettingwater_time",
                  "water_sufficient_lastmonth",
                  "stagnant_water_near",
                  "people_using_latrines",
                  "barriers_usetoilets",
                  "waste_disposal",
                  "handwashing_access"
      )

  }

  df_h2r_cols <- input_df |>
    # select(any_of(purrr::map_chr(h2r_cols, ~.x))) |>
    select(contains(h2r_cols)) |>
    mutate(country_code = country_code)
  return(df_h2r_cols)
}


#' load_h2r_indictors
#'
#' @return
#' @export
#' @description combination of `load_h2r_data` and `select_h2r_indicators` to quicky load only data with only relelvant indicators
#' @examples
load_h2r_indicators <-  function(ctry_code = "som"){
  df <-load_h2r_data(main_folder_path = Sys.getenv("SOM_2203_WASH_DATA"), 
                     data_path = "data/202209/h2r_aggregated/SOM1901_H2R_hex_400km_May_2022.csv")
  
  df_processed <-  df |> 
    select_h2r_indicators(country_code = ctry_code)
  return(df_processed)  
}

```


```{r, echo=FALSE}

df_som_data <- load_h2r_indicators(ctry_code = "som")

df_som_data_shape <- som_hex |> 
  left_join(df_som_data, by = c("GRID_ID" = "hex_4000km"))


df_water_points_shape <- load_swp() |> 
  st_as_sf(coords = c("longitude","latitude"), crs = 4326)


# I want to clip the point file to just H2R areas mainly so that we can use the {leaflet} label functionality which doesn't work in {leafgl}
h2r_bbox <- som_hex |> 
  filter(GRID_ID %in% df_som_data$hex_4000km) |> 
  st_bbox() |> 
  st_as_sfc()

swp_in_h2r_bbox<-df_water_points_shape[h2r_bbox,]
swp_in_h2r_bbox_functional <- swp_in_h2r_bbox |> 
  mutate(
    functioning= tolower(functioning)
  ) |> 
  filter(functioning=="yes")

df_som_data_polygons <- sf::st_cast(x = df_som_data_shape,to = 'POLYGON')[h2r_bbox,]

```

### H2R idp_pull_factors_access_water_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_access_water_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_access_food_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_access_food_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_better_security_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_better_security_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_presence_jobs_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_presence_jobs_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_availability_shelters_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_availability_shelters_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R idp_pull_factors_better_services_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_better_services_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```
