---
title: "aa-hex_maps_with_water_points"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{aa-hex_maps_with_water_points}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  collapse = TRUE,
  comment = "#>",
  warning = F, 
  message = F
)
```

```{r, echo=FALSE}
library(here)
library(tidyverse)
devtools::load_all()
theme_set(theme_bw())
library(sf)
library(tmap)
library(leaflet)
```


```{r, echo=FALSE}

df_som_data <- load_h2r_indicators(main_folder_path =  Sys.getenv("SOM_2203_WASH_DATA"), 
                                   data_path = "data/202209/h2r_aggregated/SOM1901_H2R_hex_400km_May_2022.csv", 
                                   ctry_code = "som")

df_som_data_shape <- som_hex |> 
  left_join(df_som_data, by = c("GRID_ID" = "hex_4000km"))


df_water_points_shape <- load_swp() |> 
  st_as_sf(coords = c("longitude","latitude"), crs = 4326)


# I want to clip the point file to just H2R areas mainly so that we can use the {leaflet} label functionality which doesn't work in {leafgl}
h2r_bbox <- som_hex |> 
  filter(GRID_ID %in% df_som_data$hex_4000km) |> 
  st_bbox() |> 
  st_as_sfc()

swp_in_h2r_bbox<-df_water_points_shape[h2r_bbox,]
swp_in_h2r_bbox_functional <- swp_in_h2r_bbox |> 
  mutate(
    functioning= tolower(functioning)
  ) |> 
  filter(functioning=="yes")

df_som_data_polygons <- sf::st_cast(x = df_som_data_shape,to = 'POLYGON')[h2r_bbox,]

```
# H2R Hex Maps with strategic water points {.tabset}

## Main Water Sources

### H2R mainsource_water_borehole with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_borehole",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R mainsource_water_well_unprotected with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_well_unprotected",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R mainsource_water_kiosk with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_kiosk",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R mainsource_water_publictap with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_publictap",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R mainsource_water_spring_unprotected with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_spring_unprotected",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R mainsource_water_rainwater with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_rainwater",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R mainsource_water_surface with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "mainsource_water_surface",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```
## Getting water time

### H2R gettingwater_time_30_to_1 with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "gettingwater_time_30_to_1",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R gettingwater_time_more1_to_halfday with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "gettingwater_time_more1_to_halfday",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R gettingwater_time_under_30 with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "gettingwater_time_under_30",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R gettingwater_time_more_halfday with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "gettingwater_time_more_halfday",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```
## IDP Pull factors

### H2R idp_pull_factors_access_water_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_access_water_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_access_food_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_access_food_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_better_security_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_better_security_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_presence_jobs_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_presence_jobs_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")

```

### H2R idp_pull_factors_availability_shelters_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_availability_shelters_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R idp_pull_factors_better_services_yes with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "idp_pull_factors_better_services_yes",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

## IDP Push factors

### H2R hc_push_main_conflict with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_conflict",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R hc_push_main_drought with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_drought",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R hc_push_main_failed rains with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_failed rains",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R hc_push_main_flooding with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_flooding",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R hc_push_main_lack_food with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_lack_food",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```

### H2R hc_push_main_lack_water with strategic water data

```{r, echo=FALSE, fig.height=8, fig.width=10}

map_leaflet_polygon_and_point(input_polygon_layer = df_som_data_polygons,
                              polygon_lyr_column = "hc_push_main_lack_water",
                              input_point_layer = swp_in_h2r_bbox_functional,
                              point_lyr_column = "water_source_type")
```
