---
title: "aa-selecting_assessment_indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-selecting_assessment_indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(here)
library(tidyverse)
# library(somaliaWASH)
devtools::load_all()
```

## Intro
Suggest following a [markdown first](https://rtask.thinkr.fr/when-development-starts-with-documentation/) approach to this analysis.

## Loading and selecting data

Following the markdown first approach you would write the functions directly in the markdown chunk below and then demonstrate how they work in the subsequent chunk. Once you are confident they are working as desired. Copy the functions to new files in the `R/` folder and remove this chunk leaving only the example demonstration here:

```{r}

#' load_h2r_data
#'
#' @param main_folder_path 
#' @param data_path 
#'
#' @return
#' @export
#' @description function to load H2R data set - will use environment key to specify base data directory
#' @examples
load_h2r_data <-  function(main_folder_path, data_path){
  
  # main_folder_path <-  Sys.getenv("SOM_2203_WASH_DATA")
  # data_path <- "data/202209/raw/REACH_H2R_0522-2607_data2.csv"
  
  h2r_data <- readr::read_csv(file.path(main_folder_path, data_path))
  
  return(h2r_data)
}

#' select_h2r_indicators
#'
#' @param input_df 
#' @param country_code 
#'
#' @return
#' @export
#' @description function to select relevant h2r indicators from data set
#' @examples
select_h2r_indicators <- function(input_df, country_code="som"){
  if(country_code=="som"){
    h2r_cols <- c("hex_4000km",
                  "climatic_shock",
                  "crop_loss_reasons",
                  "primary_reason_moved",
                  "idp_new_arrivals",
                  "idp_arrived_reason",
                  "idp_pull_factors",
                  "hc_push_main",
                  "mainsource_water",
                  "responsible_water_fetching",
                  "surfacewater_drinking",
                  "gettingwater_time",
                  "water_sufficient_lastmonth",
                  "stagnant_water_near",
                  "people_using_latrines",
                  "barriers_usetoilets",
                  "waste_disposal",
                  "handwashing_access"
    )
  }
  
  df_h2r_cols <- input_df |>
    # select(any_of(purrr::map_chr(h2r_cols, ~.x))) |>
    select(contains(h2r_cols)) |>
    mutate(country_code = country_code)
  return(df_h2r_cols)
}


#' load_h2r_indictors
#'
#' @param main_folder_path 
#' @param data_path 
#' @param ctry_code 
#'
#' @return
#' @export
#' @description combination of `load_h2r_data` and `select_h2r_indicators` to quicky load only data with only relelvant indicators
#' @examples
load_h2r_indicators <-  function(main_folder_path, data_path, ctry_code="som"){
  df <-load_h2r_data(main_folder_path, data_path)

  df |>
    select_h2r_indicators(country_code=ctry_code)

}

```


## Finding the appropriate data set:

Have a look at all the datasets available in the project.

```{r}

# data set list (?ds_ls())
ds_ls()

```

use shortened easy to remember names to access file paths:

```{r}
# ?ds_find() - stands for data set find
ds_find(ds = "2205_h2r_settlement")

```


this can be wrapped in various load functions like `load_swp()` which loads the Strageic Water Point data.
`TODO:` not priority, but later we can refactor code to just have one `load_*()` function which loads correct data based on argument
```{r}

swp <-  load_swp()
```



# simple point aggregations to grid


```{r}

swp_sf <- swp |>
     sf::st_as_sf(coords=c("longitude","latitude"), crs=4326)

 # just aggregate point counts
wp_n_grid_utm <- swp_sf |>
    hex_aggregate_pt_count(hex = som_hex)

# aggregate point counts based on `var`- `val` combination
swp_n_grid_utm <- swp_sf |>
    hex_aggregate_pt_count(hex = som_hex,var = "is_strategic",var_val = "yes")

```

let's just map for fun
```{r}
library(leaflet)
library(leafgl) # for faster rendering large polygon datasets

# for leaflet - convert back to wgs84

wp_n_grid <- wp_n_grid_utm |> 
  sf::st_transform(crs= 4326) |> 
  sf::st_cast("POLYGON") # just leafgl can't handle multipolygons

leaflet() |> 
  addTiles() |> 
  leafgl::addGlPolygons(data = wp_n_grid,
                        fillColor = ~count,
                        popup =~count) 
  



```


```
