---
title: "aa-selecting_assessment_indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-selecting_assessment_indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(here)
library(tidyverse)
library(somaliaWASH)
```

## Intro
Suggest following a [markdown first](https://rtask.thinkr.fr/when-development-starts-with-documentation/) approach to this analysis.

## Loading and selecting data

Following the markdown first approach you would write the functions directly in the markdown chunk below and then demonstrate how they work in the subsequent chunk. Once you are confident they are working as desired. Copy the functions to new files in the `R/` folder and remove this chunk leaving only the example demonstration here:

```{r}

#' load_h2r_data
#'
#' @return
#' @export
#' @description function to load H2R data set - will use environment key to specify base data directory
#' @examples
load_h2r_data <-  function(){
  
}

#' select_h2r_indicators
#'
#' @return
#' @export
#' @description function to select relevant h2r indicators from data set
#' @examples
select_h2r_indicators <- function(){
  
}


#' load_h2r_indictors
#'
#' @return
#' @export
#' @description combination of `load_h2r_data` and `select_h2r_indicators` to quicky load only data with only relelvant indicators
#' @examples
load_h2r_indicators <-  function(){
  df <-load_h2r_data()
  df |> 
    select_h2r_indicators()
}

```


```{r}


```
